The \dealii Library, Version 9.5

### 2023-12-28 9.5/paper.tex
Make the list of contributors easier to read in the flow of
the paper.

% This is up-to-date as of 2023-06-26 7:00pm central

Pasquale    Africa,
Nicolas     Barnafi,
Nistha      Bhawsinka,
Bruno       Blais,
Fabian      Castelli,
Terry       Cojean,
Niklas      Fehn,
Emmanuel    Ferdman,
Vadim       Gallyamov,
Daniel      Garcia-Sanchez,
Rene        Gassmoeller,
Robin       Goermer,
Graham      Harper,
Quang       Hoang,
Sean        Ingimarson,
Vladimir    Ivannikov,
Pengfei     Jia,
Tao         Jin,
Nils        Margenberg,
Luz         Paz,
Laura       Prieto Saavedra,
Sebastian   Proell,
Ce          Qin,
Oleg        Rogozin,
Andrew      Salmon,
Michael     Schlottke-Lakemper,
Christoph   Schmidt,
Magdalena   Schreter-Fleischhacker,
Richard     Schussnig,
Nils        Schween,
Ahmad       Shahba,
Simon       Sticko,
Buğrahan    Temür,
Ivy         Weber,
Niklas      Wik,
Vladimir    Yushutin,
Jiaqi       Zhang.

Their contributions are much appreciated!

>>>>

% This is up-to-date as of 2023-06-26 7:00pm central
\begin{quote}
Pasquale    Africa,
Nicolas     Barnafi,
Nistha      Bhawsinka,
Bruno       Blais,
Fabian      Castelli,
Terry       Cojean,
Niklas      Fehn,
Emmanuel    Ferdman,
Vadim       Gallyamov,
Daniel      Garcia-Sanchez,
Rene        Gassmoeller,
Robin       Goermer,
Graham      Harper,
Quang       Hoang,
Sean        Ingimarson,
Vladimir    Ivannikov,
Pengfei     Jia,
Tao         Jin,
Nils        Margenberg,
Luz         Paz,
Laura       Prieto Saavedra,
Sebastian   Proell,
Ce          Qin,
Oleg        Rogozin,
Andrew      Salmon,
Michael     Schlottke-Lakemper,
Christoph   Schmidt,
Magdalena   Schreter-Fleischhacker,
Richard     Schussnig,
Nils        Schween,
Ahmad       Shahba,
Simon       Sticko,
Buğrahan    Temür,
Ivy         Weber,
Niklas      Wik,
Vladimir    Yushutin,
Jiaqi       Zhang.
\end{quote}
Their contributions are much appreciated!
